\chapter{Calculation Parameters}
\label{Ch:CalcParameters}

GMAT's Central Body (Cb)\index{Cb} and Coordinate System
(CS)\index{CS} dependent parameters were tested to verify that the
internal calculations were correct. In order to minimize the effects
of other forces/elements, the two-body cases from the Propagators
section were used, with some modification, to test both the central
body and coordinate system parameters. The only changes to the two
body cases were in the report output intervals and report output
parameters. Data was outputted in ten minute intervals. The
ISS\index{ISS} two-body case was used for the Earth case and each
planets respective two-body case was used for the non-Earth cases.

\section{Initial Orbit State Conditions}
The ISS\index{ISS}, GEO\index{GEO}, Mars1, Mercury1, Moon, Neptune1,
Pluto1, Saturn1, Uranus1 and Venus1 two-body case's initial orbit
parameters were used from the Propagation\index{Propagation} section
(Chapter~\ref{Ch:Propagators}) for the test cases in this section.

Refer to Appendix ~\ref{Sec:initCondsProp} Tables~\ref{Table:
InitStateISS}-~\ref{Table: InitStateVenus} for a listing of all
Propagator initial orbit states used for the Calculation Parameter
test cases.

\section{Central Body Dependent Parameters}
\subsection{Naming Convention}
\label{nameConvCb}
\input{NamingConventionCb.tex}

\subsection{Comparison Script Information}
Comparison\_Tool1\_Tool2\_Cb.m is the script used to perform the
coordinate system comparisons needed for the Acceptance Test Plan.
Many elements of this script were extracted from the
Comparison\_Tool1\_Tool2\_CS.m script.

Comparison\_Tool1\_Tool2\_Cb.m was designed to allow the user to
select two programs to compare to one another. The comparison
involves taking the difference of the variables listed in the
Acceptance Test Plan Overview Chapter-$>$Testing
Methodology-$>$Calculation Parameters section.

Refer to Appendix~\ref{Ch:CompScripts} for more details on this
script and others used in the Acceptance Test Plan document.

\subsection{Test Case Results}
The following results are for the Central Body-Calculation Parameter
section. The current GMAT Build is compared to STK\index{STK} and
FreeFlyer\index{FreeFlyer} for this section.

FF-STK comparison results presented in Tables~\ref{Table: FF-STK CB
Parameters Set 1}-~\ref{Table: FF-STK CB Parameters Set 5} are used
as a way to determine if the GMAT comparison values are acceptable.
If GMAT comparison data is within the same order of magnitude as the
FF-STK comparison data, that is acceptable. A more detailed
acceptance metric/matrix will be developed at a later date.

\input{../GMAT-STK-CbParams-1.tex}\index{STK}
\input{../GMAT-STK-CbParams-2.tex}\index{STK}
\input{../GMAT-STK-CbParams-3.tex}\index{STK}
\input{../GMAT-STK-CbParams-4.tex}\index{STK}
\input{../GMAT-STK-CbParams-5.tex}\index{STK}
\clearpage

\input{../FF-GMAT-CbParams-1.tex}\index{FreeFlyer}
\input{../FF-GMAT-CbParams-2.tex}\index{FreeFlyer}
\input{../FF-GMAT-CbParams-3.tex}\index{FreeFlyer}
\input{../FF-GMAT-CbParams-4.tex}\index{FreeFlyer}
\input{../FF-GMAT-CbParams-5.tex}\index{FreeFlyer}
\clearpage

\input{../FF-STK-CbParams-1.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CbParams-2.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CbParams-3.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CbParams-4.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CbParams-5.tex}\index{STK}\index{FreeFlyer}
\clearpage

\subsection{Win/Mac GMAT Comparison}
\input{../GMAT-MacGMAT-CbParams-1.tex}
\input{../GMAT-MacGMAT-CbParams-2.tex}
\input{../GMAT-MacGMAT-CbParams-3.tex}
\input{../GMAT-MacGMAT-CbParams-4.tex}
\input{../GMAT-MacGMAT-CbParams-5.tex}
\clearpage

\subsection{Win/Linux GMAT Comparison}
\input{../GMAT-LinuxGMAT-CbParams-1.tex}
\input{../GMAT-LinuxGMAT-CbParams-2.tex}
\input{../GMAT-LinuxGMAT-CbParams-3.tex}
\input{../GMAT-LinuxGMAT-CbParams-4.tex}
\input{../GMAT-LinuxGMAT-CbParams-5.tex}

\section{Coordinate System Dependent Parameters}
\subsection{Naming Convention}
\label{nameConvCS}
\input{NamingConventionCS.tex}

\subsection{Comparison Script Information}
The script used to perform the Coordinate System comparisons needed
for the Acceptance Test Plan is Comparison\_Tool1\_Tool2\_CS.m. Many
elements of this script were extracted from the
Comparison\_Tool1\_Tool2\_PV.m script.

Comparison\_Tool1\_Tool2\_CS.m was designed to allow the user to
select two programs to compare to one another. The comparison
involves taking the difference of the variables listed in the
Acceptance Test Plan Overview Chapter-$>$Testing
Methodology-$>$Calculation Parameters section.

Refer to Appendix~\ref{Ch:CompScripts} for more details of this
script and others used in the Acceptance Test Plan document.

\subsection{Test Case Results}
The following results are for the Coordinate System-Calculation
Parameter section. The current GMAT Build is compared to
STK\index{STK} and FreeFlyer\index{FreeFlyer} for this section.

 FF-STK comparison results presented in
Tables~\ref{Table: FF-STK CS Parameters Set 1}-~\ref{Table: FF-STK
CS Parameters Set 5} are used as a way to determine if the GMAT
comparison values are acceptable. If GMAT comparison data is within
the same order of magnitude as the
FF-STK\index{FreeFlyer}\index{STK} comparison data that is
acceptable. A more detailed acceptance metric/matrix will be
developed at a later date.

\input{../GMAT-STK-CSParams-Pos.tex}\index{STK}
\input{../GMAT-STK-CSParams-Vel.tex}\index{STK}
\input{../GMAT-STK-CSParams-H.tex}\index{STK}
\input{../GMAT-STK-CSParams-VelVec.tex}\index{STK}
\input{../GMAT-STK-CSParams-Angle.tex}\index{STK}
\clearpage

\input{../FF-GMAT-CSParams-Pos.tex}\index{FreeFlyer}
\input{../FF-GMAT-CSParams-Vel.tex}\index{FreeFlyer}
\input{../FF-GMAT-CSParams-H.tex}\index{FreeFlyer}
\input{../FF-GMAT-CSParams-VelVec.tex}\index{FreeFlyer}
\input{../FF-GMAT-CSParams-Angle.tex}\index{FreeFlyer}
\clearpage

\input{../FF-STK-CSParams-Pos.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CSParams-Vel.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CSParams-H.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CSParams-VelVec.tex}\index{STK}\index{FreeFlyer}
\input{../FF-STK-CSParams-Angle.tex}\index{STK}\index{FreeFlyer}
\clearpage

\subsection{Win/Mac GMAT Comparison}
\input{../GMAT-MacGMAT-CSParams-Pos.tex}
\input{../GMAT-MacGMAT-CSParams-Vel.tex}
\input{../GMAT-MacGMAT-CSParams-H.tex}
\input{../GMAT-MacGMAT-CSParams-VelVec.tex}
\input{../GMAT-MacGMAT-CSParams-Angle.tex}
\clearpage

\subsection{Win/Linux GMAT Comparison}
\input{../GMAT-LinuxGMAT-CSParams-Pos.tex}
\input{../GMAT-LinuxGMAT-CSParams-Vel.tex}
\input{../GMAT-LinuxGMAT-CSParams-H.tex}
\input{../GMAT-LinuxGMAT-CSParams-VelVec.tex}
\input{../GMAT-LinuxGMAT-CSParams-Angle.tex}
\clearpage
