\chapter{Integrators} \label{Ch:Integrators}
GMAT's integrators were tested on a system level in order to verify
that all the integrators were working correctly. In order to
minimize the effects of other forces/elements, the two-body cases
from the Propagators section were used, with some modification, for
testing the integrators. The report output interval and integrators
were the only parameter changed when using the Propagator two body
test cases. Data was outputted in ten minute intervals.

\section{Initial Orbit Conditions}
The ISS\index{ISS} and GEO\index{GEO} two-body case's initial orbit
parameters were used from the Propagation\index{Propagation} section
(Chapter~\ref{Ch:Propagators}) for the test cases in this section.

Refer to Appendix ~\ref{Sec:initCondsProp} Tables~\ref{Table:
InitStateISS}-~\ref{Table: InitStateVenus} for a listing of all
Propagation\index{Propagation} initial orbit states used for the
Integrator test cases.

\section{Naming Convention}
\label{nameConvInteg}
\input{NamingConventionInteg.tex}

\section{Comparison Script Information}
Comparison\_Integ.m is the script used to perform the integrator
comparisons needed for the Integrators section of the Acceptance
Test Plan. This script was designed to allow the user to select a
GMAT Build or the exact analytic solution to compare to one
another.\\

Refer to Appendix~\ref{Ch:CompScripts} for more details about this
script and others used in the Acceptance Test Plan document.
\clearpage

\section{Test Case Results}
The following results are for the Integrator section. The GMAT
Integrator results are being compared to an exact analytical
two-body solution. We'd like the comparison data to be as close to
zero as possible. A detailed acceptance metric/matrix will be
developed at a later date.

\input{../Exact-GMAT-Integrator-GEO.tex}
\input{../Exact-GMAT-Integrator-ISS.tex}

\subsection{Win/Mac GMAT Comparison}
\input{../GMAT-MacGMAT-Integrator-GEO.tex}
\input{../GMAT-MacGMAT-Integrator-ISS.tex}

\clearpage
\subsection{Win/Linux GMAT Comparison}
\input{../GMAT-LinuxGMAT-Integrator-GEO.tex}
\input{../GMAT-LinuxGMAT-Integrator-ISS.tex}
