This section describes the naming convention for Performance scripts
and output reports generated for use in GMAT's Acceptance Test Plan.
The naming convention consists of an ordered series of option
strings, separated by underscores (\_ ). Currently, options are
allowed for the following fields, and will be present in the file
name in order:
\begin{enumerate}
  \item \emph{tool} - Tool used to generate the trajectory.
  \item \emph{traj} - Type of trajectory.
  \item \emph{forces} - Forces applied.
  \item \emph{output} - Flag noting if there is output.
\end{enumerate}

The word Performance precedes the \emph{tool} field. The final
stopping condition file format is as followed:\\
Performance\_\emph{tool}\_\emph{traj}\_\emph{forces}\_\emph{output}.report or\\
Performance\_\emph{tool}\_\emph{traj}PM\_\emph{forces}\_\emph{output}.report

The \emph{tool} field should always be the first option field.
Future additional fields should be added to the end of the list of
fields. Each field has a finite list of options, as follows (future
options should be added to this list):
\begin{enumerate}
  \item \emph{tool}
  \begin{tabular}{ll}
    STK  & - Satellite Toolkit HPOP or Astrogator\\
    FF   & - FreeFlyer\\
    GMAT & - General Mission Analysis Tool\\
    OD   & - Orbital Determination Toolbox\\
  \end{tabular}

  \item \emph{traj}
  \begin{tabular}{ll}
    Deepspace & - deep space orbit\\
    EML2      & - Earth Moon L2 orbit\\
    GEO       & - GEO orbit\\
    GPS       & - MEO orbit\\
    ISS       & - LEO orbit\\
    Mars1     & - eccentric low orbit\\
    Molniya   & - HEO orbit\\
    Moon      & - eccentric low orbit\\
    SunSync   & - LEO orbit\\
  \end{tabular}

NOTE:  Some test cases contain \emph{traj} variations. In this case
\emph{traj} precedes the modification. For example, an ISS
trajectory is used and the point mass code is used in GMAT instead
of JGM2 0x0. In this case the \emph{traj} is ISSPM.

  \item \emph{forces}
  \begin{tabular}{ll}
    AllPlanets  & - Sun, Mercury, Venus, Earth, Moon, Mars, Mercury, Jupiter,\\
    &   and Pluto point mass gravity included.\\
    1PM         & - Central body is the only point mass included.\\
    Drag        & - JR is used for Earth cases.\\
    NSG         & - JGM2 20x20 is used.\\
    SRP         & - SRP is turned on
  \end{tabular}
\end{enumerate}
