This section describes the naming convention for coordinate system
dependent parameter scripts and output reports. The naming
convention consists of a case sensitive ordered series of option
strings, separated by underscores (\_ ). Currently, options are
allowed for the following fields, and will be present in the file
name:
\begin{enumerate}
  \item \emph{tool} - The tool used to generate the test case
  \item \emph{traj} - The trajectory to use.  This includes initial conditions, physical parameters, and time step
  \item \emph{CS} - The coordinate system to use. The celestial
  body to use is followed by the CS in the name
\end{enumerate}

CSParams precedes the \emph{tool} field and 2Body precedes the
\emph{CS} field. The final CS file format is as followed:\\
CSParams\_\emph{tool}\_\emph{traj}\_2Body\_\emph{CS}.report\\

The \emph{tool} field should always be the first option field. Each
field has a finite list of options, as follows (future options
should be added to this list):
\begin{enumerate}
  \item \emph{tool}\\
  \begin{tabular}{ll}
    STK  & - Satellite Toolkit HPOP or Astrogator\\
    FF   & - FreeFlyer\\
    GMAT & - General Mission Analysis Tool\\
  \end{tabular}

  \item \emph{traj}\\
  \begin{tabular}{ll}
    ISS & - leo orbit\\
    SunSync & - leo orbit\\
    GPS & - meo orbit\\
    GEO & - geo orbit\\
    Molniya & - heo orbit\\
    Mars1 & - eccentric low orbit\\
    Mercury1 & - eccentric low orbit\\
    Moon & - eccentric low orbit\\
    Pluto1 & - eccentric low orbit\\
    Venus1 & - eccentric low orbit\\
  \end{tabular}

NOTE:  Some test cases contain \emph{traj} variations. In this case
\emph{traj} precedes the modification. For example, if ISS
trajectory is needed with no output, then \emph{traj} can be
ISSnoOut. The lack of a report file is shortened to noOut.

  \item \emph{CS}\\
  \begin{tabular}{lll}
    EarthFixed & EarthMJ2000Eq & EarthMJ2000Ec\\
    EarthTODEq & EarthTODEc & EarthMODEq\\
    EarthMODEc & EarthGSM & EarthGSE\\
    MarsFixed & MarsMJ2000Eq & MarsMJ2000Ec\\
    MercuryFixed & MercuryMJ2000Eq & MercuryMJ2000Ec\\
    MoonFixed & MoonMJ2000Eq & MoonMJ2000Ec\\
    NeptuneFixed & NeptuneMJ2000Eq & NeptuneMJ2000Ec\\
    PlutoFixed & PlutoMJ2000Eq & PlutoMJ2000Ec\\
    SaturnFixed & SaturnMJ2000Eq & SaturnMJ2000Ec\\
    UranusFixed & UranusMJ2000Eq & UranusMJ2000Ec\\
    VenusFixed & VenusMJ2000Eq & VenusMJ2000Ec\\
  \end{tabular}

\end{enumerate}
