\chapter{Professional Advancements}
\label{Ch:ProfAdvances}

\section{Professional Intern Program (PIP) I Work}

\subsection{Edwin Dove}
\subsubsection{Introduction}
In July of 2005, Edwin Dove obtained a full-time position as a
Flight Dynamics Analysis Branch (FDAB) engineer and began PIP1 work
on the Acceptance Test Plan tests and documentation. He worked
alongside his mentor, Steve Hughes of the FDAB, and the GMAT
development team, which consists of Code 595, Code 583, and
contractor support. Steve presented Edwin with the framework of the
Acceptance Test Plan, Edwin built upon that initial framework, and
the results are presented in this document.

\subsubsection{Personal Improvements}
One of the most difficult tasks Edwin had was to make the
comparisons between programs as equivalent as possible. Many
programs, such as STK and FF, don't have documentation available on
how their software works underneath their Graphical User Interface
(GUI). Improvements in his communication skills were seen as he
gathered information on the various components of the different
software programs.

Learning how to output some of the STK and FF parameters needed to
compare to GMAT was another complicated task for Edwin. The methods
for outputting certain parameters, such as velocity at apoapsis and
the Mean Hour Angle (MHA) of other planets, were not straight
forward and often required some non-intuitive manipulations of the
programs.

In an attempt to simplify the comparison process between GMAT and
reference software packages [Satellite Tool Kit (STK) and FreeFlyer
(FF)], Edwin chose to use MATLAB scripts to perform comparisons. He
was able to use the ability to connect to GMAT, STK, and Excel from
MATLAB to his advantage, saving time in rerunning tests and
providing up to date results.

This PIP project also provided a way to have Edwin engage in open
communication with the GMAT development team, and STK and FF
representatives. A system of submitting GMAT issues through an Excel
spreadsheet worked well for the team in the beginning of development
until a more advanced setup through Bugzilla was used. Edwin was
able to submit GMAT issues he noticed and make suggestions for
improvement to the software. Good communication skills are important
for ones personal and professional advancement, and it is something
that develops with experience.

\subsubsection{Lessons Learned}
Creating reports take a long time and patience!!!\\
STK's way of outputting parameters is complicated and time consuming.\\
COTS software is not fully documented for the consumer. Requests for math specifications waste valuable time.\\
